Exploring mutation-induced protein fold switching using multisequence Monte Carlo simulations

### 2017-05-11 Manuscript.tex
minor

\begin{table}
\caption{\label{tab:table1} Model sequences of different sequence lengths $N$ studied in this work. In addition to the 6 sequences listed, we studied sets of 1,024 sequences derived from the A1-N1 and A2-TN pairs, respectively, (see text) denoted S16 and S35, respectively, and a restricted S16-set of 144 sequences denoted $\mathrm{S16}_{144}$ (also studied in Ref.~\protect\citep{Holzgrafe2014}).  }
\begin{ruledtabular}
\begin{tabular}{lcr}
Name & $N$ & Sequence\\
\hline
N1 & 16 & phphphpttphphphp \\
A1 & 16 & pphpphhpphpphhpp \\
Ran1 & 16 & \textbf{(add)}\\
Ran2 & 16 &  \textbf{(add)}\\
A2 & 35 & A1-ttt-A1\\
TN & 35 & A1-ttt-N1\\
\end{tabular}
\end{ruledtabular}
\end{table}

@@

\begin{table}
\caption{\label{tab:table1} List of simulations carried out in this work. }
\begin{ruledtabular}
\begin{tabular}{lccccr}
Runs & Algorithm & $T$ & MC steps &  Sequence set\\
\hline
32$\times$4\footnote{32 runs carried out for each of the 4 sequences. } & ST & $8\times 10^6$ &A1,N1,Ran1,Ran3\\
32$\times$8\footnote{32 independent runs carried out at each of the temperatures $T_1$ to $T_8$} & MS & $144\times 10^6$ & 16 &$\mathrm{S16}_{144}$\\
16 & MS & $5\times 10^9$ & 16 & S16 \\
16 & MS & $4\times 10^9$ & 35 & S35 \\
\end{tabular}
\end{ruledtabular}
\end{table}

>>>>

\begin{table}
\caption{\label{tab:table1} Model sequences of different sequence lengths $N$ studied in this work. In addition to the 6 sequences listed, we studied sets of 1,024 sequences derived from the A1-N1 and A2-TN pairs, respectively, (see text) denoted S16 and S35, respectively, and a restricted S16-set of 144 sequences denoted $\mathrm{S16}_{144}$ (also studied in Ref.~\protect\citep{Holzgrafe2014}).  }
\begin{ruledtabular}
\begin{tabular}{lcr}
Name & $N$ & Sequence\\
\hline
N1 & 16 & phphphpttphphphp \\
A1 & 16 & pphpphhpphpphhpp \\
R1 & 16 & \textbf{(add)}\\
R2 & 16 &  \textbf{(add)}\\
A2 & 35 & (A1)ttt(A1)\\
TN & 35 & (A1)ttt(N1)\\
\end{tabular}
\end{ruledtabular}
\end{table}

@@

\begin{table}
\caption{\label{tab:table1} List of simulations carried out in this work. }
\begin{ruledtabular}
\begin{tabular}{lccccr}
Runs & Algorithm & $\kb T$  & MC steps &  Sequences\\
\hline
32 & ST & 0.43--0.65 & $8\times 10^6$ &A1\\ 
32 & ST & 0.43--0.65 & $8\times 10^6$ &N1\\ 
32 & ST & 0.43--0.65 & $8\times 10^6$ &R1\\ 
32 & ST & 0.43--0.65 & $8\times 10^6$ &R2\\ 
32$\times$8\footnote{32  runs per temperature for 8 temperatures in the range given.} & MS &0.43--0.65& $144\times 10^6$ & $\mathrm{S16}_{144}$\\
16 & MS & 0.43  & $5\times 10^9$ &  S16 \\
16 & MS & 0.46 & $4\times 10^9$ &  S35 \\
\end{tabular}
\end{ruledtabular}
\end{table}
